ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-10-02 pyked.tex
WIP respond to #42

# Create the reactor and the outside environment
reac = ct.IdealGasReactor(gas)
env = ct.Reservoir(ct.Solution('air.xml'))
\end{pythonbox}
%
To apply the effect of the volume trace to the \pybox|IdealGasReactor|, a
\pybox|Wall| is installed between the reactor and environment, and assigned
a velocity. Although we do not show the details here, a reference implementation
of a class that computes a wall velocity given the volume history of the reactor
is available in CanSen~\autocite{cansen}, in the
\pybox|cansen.profile.VolumeProfile| class. Then, a Cantera \pybox|ReactorNet|
can be used to advance the state through autoignition, in this case to an end
time of \SI{50}{\milli\second}:
%
\begin{pythonbox}
time = dp.volume_history.time
volume = dp.volume_history.volume
ct.Wall(reac, env, velocity=VolumeProfile(time=time, volume=volume))

>>>>

# Create the reactor and the outside environment
reac = ct.IdealGasReactor(gas)
env = ct.Reservoir(ct.Solution('air.xml'))
\end{pythonbox}
%
In this example, \pybox|reac| represents the contents of the RCM reaction chamber and \pybox|env|
represents the contents of the environment. \verb|air.xml| is an input file included with Cantera
that represents an average composition of air. To apply the effect of the volume trace to the
\pybox|IdealGasReactor|, a \pybox|Wall| is installed between the reactor and environment and
assigned a velocity. The \pybox|Wall| allows the environment to do work on the reactor (or vice
versa) and change the reactor's thermodynamic state; we use a \pybox|Reservoir| for the environment
because in Cantera, \pybox|Reservoir|s always have a constant thermodynamic state and composition.
Using a \pybox|Reservoir| accelerates the solution compared to using two \pybox|IdealGasReactor|s,
since the composition and state of the environment are typically not necessary for the solution of
auotignition problems. Although we do not show the details here, a reference implementation of a
class that computes a wall velocity given the volume history of the reactor is available in
CanSen~\autocite{cansen}, in the \pybox|cansen.profile.VolumeProfile| class. Then, a Cantera
\pybox|ReactorNet| can be used to advance the state through autoignition, in this case to an end
time of \SI{50}{\milli\second}:
%
\begin{pythonbox}
time = dp.volume_history.time
volume = dp.volume_history.volume
ct.Wall(reac, env, velocity=VolumeProfile(time=time, volume=volume))
